% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[a4paper]{article}
% \usepackage{fontspec}
% \setmainfont{TeX Gyre Termes}
\usepackage[T1]{fontenc}
\usepackage{libertine}
% \usepackage[libertine]{newtxmath}
\usepackage{inconsolata}
\usepackage{hyperref}
\usepackage[left=2.25cm, right=2.25cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}
\usepackage[UKenglish]{babel}
% \usepackage[UKenglish]{isodate}
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=1000
\clubpenalty=1000

% Set your name here
\def\name{Danilo Freire}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://danilofreire.github.io/DaniloFreireCV.pdf}

% The following metadata will show up in the PDF properties
\hypersetup{
	colorlinks = true,
	urlcolor = darkblue,
	pdfauthor = {Danilo Freire},
	pdfkeywords = {},
	pdftitle = {Danilo Freire: Curriculum Vitae},
	pdfsubject = {},
	pdfpagemode = UseNone
}

% Customise page headers
\pagestyle{myheadings}
\markright{Danilo Freire}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
	\begin{list}{}{
			\setlength{\leftmargin}{1.5em}
		}
		}{
	\end{list}
}

\begin{document}

% Place name at left
{\huge \bf \name}

% Alternatively, print name centred and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
	Emory University\\
    Department of Data and Decision Sciences\\
	36 Eagle Row, 4\textsuperscript{th} Floor, Room 480\\
	Atlanta, GA 30322, United States
\end{minipage}
\begin{minipage}{0.45\linewidth}
	\begin{tabular}{ll}
		Email:          & \href{mailto:danilo.freire@emory.edu}{danilo.freire@emory.edu}          \\
		Homepage:       & \href{http://danilofreire.github.io/}{http://danilofreire.github.io} \\
		GitHub:         & \href{http://github.com/danilofreire}{http://github.com/danilofreire} \\
		Google Scholar: & \href{https://tinyurl.com/df-gscholar}{https://tinyurl.com/df-gscholar}
	\end{tabular}
	\end{minipage}

\section*{Academic Appointments}

\begin{itemize}
\item Visiting Assistant Professor, Department of Data and Decision Sciences, Emory University, 2024--present.
\item Honorary Senior Fellow, School of Social and Political Sciences, University of Lincoln, 2024--present.
\item Senior Lecturer, School of Social and Political Sciences, University of Lincoln, 2021--2024.
\item Postdoctoral Research Associate, Political Theory Project, Brown University, 2018--2020.
\end{itemize}

\section*{Education}

\begin{itemize}
\item PhD in Political Economy, King's College London, 2018.
% \begin{itemize}
% \item Thesis: \textit{Essays on Political and Criminal Violence}. Supervisors: \href{http://davidskarbek.com}{David Skarbek} (Brown University) and \href{https://gabrieljleon.wordpress.com/}{Gabriel Leon} (KCL). Examination Committee: \href{http://www.econ.cam.ac.uk/people/faculty/tsa23}{Toke Aidt} (University of Cambridge) and \href{http://www.grahamdenyerwillis.com}{Graham Denyer Willis} (University of Cambridge).
% \end{itemize}
\item MA in International Relations, The Graduate Institute Geneva, 2014.
\item MA in Political Science, University of São Paulo, 2011.
\item BA in Social Sciences, University of São Paulo, 2007.
\end{itemize}

\section*{Research Interests}

\begin{itemize}
\item Substantive: Public Policy, Political Violence, Organised Crime, Collective Action, Brazilian Politics
\item Methodological: Computational Social Science, Impact Evaluation, Field Experiments, Meta-Analysis
\end{itemize}

\section*{Publications}

\subsection*{Peer-Reviewed Articles}

\begin{itemize}
\item \href{https://doi.org/10.1098/rsos.241038}{``The Reliability of Replications: A Study in Computational Reproductions''} (with Nate Breznau, Eike Mark Rinke, Alexander Wuttke and others). \textit{Royal Society Open Science}, 2025. \href{https://github.com/nbreznau/how_many_replicators}{Replication files}.
\item \href{https://doi.org/10.1111/ajps.12843}{``Legislature Size and Welfare: Evidence From Brazil''} (with Umberto Mignozzetti and Gabriel Cepaluni). Forthcoming, \textit{American Journal of Political Science}, 2024. \href{https://github.com/umbertomig/legislature-size-welfare}{Replication files}. Media coverage: \href{https://www.internationalaffairs.org.au/australianoutlook/legislature-size-and-welfare-evidence-from-brazil/}{Australian Institute of International Affairs}.
\item \href{https://doi.org/10.1177/20531680221150389}{``Vigilantism and Institutions: Attitudes toward Lynching in Brazil''} (with David Skarbek). \textit{Research \& Politics}, 2023, 10(1), 1--8. \href{https://github.com/danilofreire/lynching-experiment-brazil}{Replication files}.
\item \href{https://doi.org/10.1017/S0007123422000552}{``The Effect of Legislature Size on Distributive Politics: A Meta-Analysis''} (with Umberto Mignozzetti, Catarina Roman and Huzeyfe Alptekin). First view, \textit{British Journal of Political Science}, 2021. \href{https://github.com/danilofreire/legislature-size-meta-analysis}{Replication files}.
\item \href{http://dx.doi.org/10.1017/XPS.2020.19}{``Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries''} (with Umberto Mignozzetti and David Skarbek). \textit{Journal of Experimental Political Science}, Summer 2021, 172--184. \href{https://doi.org/10.7910/DVN/VTA5OA}{Replication files}.
\item \href{https://doi.org/10.1177%2F2053168020914444}{``Bottom-Up Accountability and Public Service Provision: Evidence from a Field Experiment in Brazil''} (with Manoel Galdino and Umberto Mignozzetti). \textit{Research \& Politics}, 2020, 7(2), 1--8. \href{https://github.com/umbertomig/tdp-accountability}{Replication files}.
\item \href{https://doi.org/10.25222/larr.447}{``congressbr: An R Package for Analysing Data from Brazil's Chamber of Deputies and Federal Senate''} (with Robert McDonnell and Guilherme Duarte). \textit{Latin American Research Review}, 2019, 54(4), 958--969. \href{https://github.com/duarteguilherme/congressbr}{Software repository}.
\item \href{https://doi.org/10.1177/0094582X19846519}{``Beasts of Prey or Rational Animals?: Private Governance in Brazil's \emph{Jogo do Bicho}''}. \textit{Latin American Perspectives}, 2019, 46(4), 230--244. Media coverage: \href{http://www.bbc.com/portuguese/brasil-40140693}{BBC Brazil}.
\item \href{https://doi.org/10.25222/larr.334}{``Evaluating the Effect of Homicide Prevention Strategies in São Paulo, Brazil: A Synthetic Control Approach''}. \textit{Latin American Research Review}, 2018, 53(2), 231--249. \href{https://github.com/danilofreire/homicides-sp-synth}{Replication files}. Media coverage: \href{http://www.valor.com.br/cultura/5111524/sangue-no-asfalto}{Valor Econômico}.
\item \href{https://doi.org/10.21105/joss.00361}{``prisonbrief: An R Package that Returns Tidy Data from the World Prison Brief Website''} (with Robert McDonnell). \textit{Journal of Open Source Software}, 2018, 3(22), 361. \href{https://github.com/danilofreire/prisonbrief}{Software repository}.
\item \href{http://www.iapss.org/wp-content/uploads/2014/10/ELA1.1_2.Lack-of-Preferences-Political-Trust-and-Education-Levels.pdf}{``Lack of Preferences, Political Trust and Education Levels: Alternative Explanations for Invalid Votes in Brazilian Elections''} (with Guilherme Arbache and Pietro Rodrigues). \textit{Encuentro Latinoamericano}, 2015, 1(1), 29--50. \href{https://github.com/danilofreire/invalid-votes-brazil}{Replication files}.
\item \href{http://recyt.fecyt.es/index.php/recp/article/view/37638}{``Between Ballot Boxes and Guns: The Competitiveness of the Executive Branch and Civil Wars, 1976-2000''}. \textit{Revista Española de Ciencia Política}, 2014, 36, 33--60. \href{https://doi.org/10.7910/DVN/NSDUYG}{Replication files}.
\end{itemize}

\subsection*{Working Papers}

\begin{itemize}
\item \href{https://github.com/danilofreire/incentives-healthcare}{``Financial Incentives and Health Care Provision: Evidence from an Experimental \textit{Aedes aegypti} Control Programme in Brazil''} (with Umberto Mignozzetti). Under review.
\item \href{https://osf.io/preprints/socarxiv/j7qta}{``The Reliability of Replications: A Study in Computational
Reproductions''} (with Nate Breznau, Eike Mark Rinke, Alexander Wuttke and others). Under review.
\item \href{https://github.com/danilofreire/danilofreire.github.io/blob/master/malapportionment.pdf}{``Legislative Outcomes and Malapportionment: Evidence from Latin America''} (with Umberto Mignozzetti and Catarina Roman).
\item \href{https://github.com/danilofreire/mercatus-analytics-papers/blob/main/automl-paper/automl.pdf}{``Democratising Policy Analytics with AutoML''}.
\item \href{https://osf.io/pzx3q}{``What Drives State-Sponsored Violence? Evidence from Extreme Bounds Analysis and Ensemble Learning Methods''} (with Gary Uzonyi).
\item Environmental Protection in Weak Party Systems: Evidence from Brazil (with Umberto Mignozzetti, in preparation).
\item Natural Disasters and Identity Reconstruction Among Syrian Refugees (with Hamoon Khelghat-Doost, in preparation).
\end{itemize}

\subsection*{Book}

\begin{itemize}
\item \href{https://github.com/danilofreire/danilofreire.github.io/blob/01dc4c9566bb5ade15b5db950046ed0a386fc5f1/texts/natural_resources_policy_choices_latam.pdf}{Natural Resources and Policy Choices in Latin America} (with Giovanna França and Umberto Mignozzetti, editors). São Paulo: Konrad Adenauer Foundation, 2020.
\end{itemize}

\subsection*{Book Chapters}

\begin{itemize}
\item \href{https://osf.io/kuqqx/}{``Prison Gangs''} (with David Skarbek). In: Griffin, Hayden; Woodward, Vanessa (ed.). \textit{Handbook of Corrections in the United States}. London: Routledge, 2017, 399--408.
\item \href{https://fnst.org/sites/default/files/uploads/2017/12/08/ngp.pdf}{``A Nova Gest\~{a}o P\'{u}blica e a Qualidade da Democracia'' {[}``The New Public Administration and the Quality of Democracy''{]}}. In: Erkens, Rainer (ed.). \textit{Nova Gest\~{a}o P\'{u}blica}. S\~{a}o Paulo: Instituto Friedrich Naumann, 2010, 9--15.
\end{itemize}

\subsection*{Other Publications}

\begin{itemize}
\item \href{https://www.kas.de/documents/273477/273526/Geopolitics+of+Renewable+Energy+in+Latin+America+-+A+Survey.pdf/9fe39ef1-6028-0836-90b0-aada31cb6769?version=1.0&t=1551887777018}{Geopolitics of Renewable Energies in Latin America: A Survey} (with Umberto Mignozzetti). 2019. Policy Report commissioned by the Konrad Adenauer Stiftung.
\item \href{https://thepoliticalmethodologist.files.wordpress.com/2016/02/tpm_v23_n1.pdf}{``Peering at Open Peer Review''}. \textit{The Political Methodologist}, 2015, 23 (1), 6--11.
\item \href{http://www.scielo.br/readcube/epdf.php?doi=10.1590/1981-38212015000300026&pid=S1981-38212015000300178&pdf_path=bpsr/v9n3/1981-3821-bpsr-9-3-0178.pdf&lang=en}{``Book Review: Causal Inference, Shaolin-Style: `Mastering Metrics' by Joshua D. Angrist and J\"{o}rn-Steffen Pischke''}. \textit{Brazilian Political Science Review}, 2015, 9 (3), 178--185.
\item \href{http://dx.doi.org/10.6084/m9.figshare.1209203}{Entering the Underworld: Prison Gang Recruitment in S\~{a}o Paulo's Primeiro Comando da Capital}. Geneva: Master's Degree Thesis in International Relations, The Graduate Institute of International and Development Studies, 2014, 97p.
\item \href{http://seer.bce.unb.br/index.php/MED/article/view/7505/6497}{``Book Review: `Why Nations Fail' by Daron Acemoglu and James Robinson''}. \textit{Meridiano47}, 2013, 14 (135).
\item \href{http://dx.doi.org/10.6084/m9.figshare.963082}{Entre Urnas e Armas: A Competitividade do Executivo e as Guerras Civis, 1976-2000 {[}Between Ballot Boxes and Guns: The Competitiveness of the Executive Branch and Civil Wars, 1976-2000{]}}. S\~{a}o Paulo: Master's Degree Thesis in Political Science, University of S\~{a}o Paulo, 2011, 204p. \href{http://dx.doi.org/10.6084/m9.figshare.963183}{Replication files}.
\end{itemize}

\section*{Software}

\begin{itemize}
  \item \href{http://danilofreire.github.io/pinochet}{pinochet: Data about the victims of the Pinochet regime, 1973-1990} (with Lucas Mingardi and Robert McDonnell).
  \item \href{https://github.com/RobertMyles/congressbr}{congressbr: Downloads, unpacks and tidies Legislative data from the Brazilian Federal Senate and Chamber of Deputies} (with Robert McDonnell and Guilherme Duarte).
  \item \href{http://danilofreire.github.io/prisonbrief}{prisonbrief: R package that returns tidy data from the World Prison Brief website} (with Robert McDonnell).
\end{itemize}

\section*{Fellowships and Awards}

\begin{itemize}
\item Research Grant, University of California, San Diego, 2024. Joint with Umberto Mignozzetti and Tereza Petrovicova (US\$ 25,000).
\item Associate Fellow (PR240832), Advance HE, 2022--present.
\item Fellow, Evidence in Governance and Politics (EGAP), 2021--present.
\item Research Grant, King's College London, 2020. Joint with David Skarbek (US\$ 10,000).
\item Research Grant, Getulio Vargas Foundation, 2019. Joint with Umberto Mignozzettt and D. Skarbek (US\$ 64,000, matching grant).
\item Research Grant, Konrad Adenauer Stiftung, 2018. Joint with Umberto Mignozzetti and D. Skarbek (US\$ 64,000).
\item Google Social Impact Challenge Grant, 2017--2019. Joint with Manuel Galdino and Umberto Mignozzetti (US\$ 300,000).
\item Adam Smith Fellowship, Mercatus Center, George Mason University, 2016--2018 (US\$ 10,000).
\item PhD Scholarship, Institute for Humane Studies, 2016--2017 (US\$ 1,500).
\item Graduate School International Research Studentship, King's College London, 2015--2018 (US\$ 58,000).
\item PhD Scholarship, Brazilian Ministry of Education, 2015--2018 (US\$ 76,000).
\item Scholarship for MA Studies, Brazilian Ministry of Education, 2009--2011.
\end{itemize}

\section*{Selected Presentations and Invited Talks}

\begin{itemize}
\item \href{https://github.com/danilofreire/lynching-experiment-brazil}{``Casting the First Stone: Attitudes Towards Lynchings in Brazil''}, University of Washington; University of Oxford; University of Notre Dame; São Paulo Military Police Academy, 2021.
\item \href{http://github.com/danilofreire/mercatus-analytics-papers}{``Democratising Policy Analytics with AutoML''}, Society for Policy Analytics, Mercatus Center, 2021.
\item \href{https://danilofreire.github.io/essex2020/aedes.html}{``Incentives in Health Care Prevention: Evidence from an Experimental Aedes Aegypti Control Programme in Brazil''}, Global South Academic Network, University of Essex, 2020.
\item \href{https://osf.io/9a6ch}{``Institutional Design and Elite Support for Climate Policies''}. APSA Annual Meeting, Washington, DC, 2019; SPSA Annual Meeting, San Juan, 2020.
\item \href{https://osf.io/9a6ch}{``Latin American Elites Favour Polycentric Governance in Climate Change Agreements''}. Annual Midwest Political Science Association Conference, Chicago, 2019.
\item \href{http://danilofreire.github.io/pcs-2019}{``What Drives State-Sponsored Violence?: Evidence from Extreme Bounds Analysis and Ensemble Learning Methods''}. Public Choice Society Annual Meeting, Louisville, 2019.
\item \href{https://www.overleaf.com/project/591ef5259fb58ede3dc4d369}{``Three Ideas from the Vienna, Virginia, and Bloomington Schools of Political Economy''}. Hayek Group Meeting, Friedrich Naumann Stiftung f{\"u}r die Freiheit and Prometheus -- Das Freiheitsinstitut, Berlin, 2017.
\item \href{https://osf.io/se2jr}{``Beasts of Prey or Rational Animals?: Private Governance in Brazil's \emph{Jogo do Bicho''}}. VI Oxbridge Conference on Brazilian Studies, University of Cambridge, 2017.
\end{itemize}

\section*{Teaching}

\begin{itemize}
\item Instructor, \href{https://danilofreire.github.io/qtm385/}{QTM 385 -- Experimental Methods} (Undergraduate). Emory University, 2024--present.
\item Instructor, \href{https://danilofreire.github.io/qtm350/}{QTM 350 -- Data Science Computing} (Undergraduate/Graduate). Emory University, 2024--present.
\item Instructor, \href{https://danilofreire.github.io/qtm151/}{QTM 151 -- Introduction to Statistical Computing II} (Undergraduate). Emory University, 2024--present.
\item Instructor (with Rosario Aguilar, Jake Bowers, Luis Maldonado, and Julia Seither) \href{https://egap.org/project/learning-days-15-latin-america-regional-hub-workshop/}{EGAP Learning Days 15: Field Experiments in the Social Sciences}. Evidence in Governance and Politics, Medellín, August 2024.
\item Instructor (with Rosario Aguilar, Jake Bowers, Luis Maldonado, and Maarten Voors) \href{https://egap.org/project/learning-days-13-latin-america-regional-hub-workshop/}{EGAP Learning Days 13: Field Experiments in the Social Sciences}. Evidence in Governance and Politics, Mexico City, August 2023.
\item Lecturer and Seminar Leader (with Anthony Ellis and Elena Gaschino), \href{https://blackboard.lincoln.ac.uk/ultra/courses/_182116_1/cl/outline}{Policing Crime and Deviance} (Undergraduate). University of Lincoln, 2021--2024.
\item Lecturer and Seminar Leader (with Nick Cowen and Aris Trantidis), \href{https://blackboard.lincoln.ac.uk/ultra/courses/_184943_1/cl/outline}{Human Rights} (Undergraduate). University of Lincoln, 2021--2024.
\item Instructor, \href{https://danilofreire.github.io/pols1824w/}{POLS 1824W -- Political Violence} (Undergraduate). Brown University, Fall 2019.
\item Instructor, \href{https://pols1600.github.io/}{POLS 1600 -- Political Research Methods} (Undergraduate). Brown University, Winter 2019.
\item Instructor, \href{https://github.com/danilofreire/economia-politica-instituicoes-ufm}{Political Economy and Institutions} (Graduate). Centro de Estudios Superiores Online de Madrid Manuel Ayau (OMMA) and Universidad Francisco Marroquín, 2017.
\item Teaching Assistant, \href{https://github.com/danilofreire/core-econ}{Principles of Economics II -- Macroeconomics} (Undergraduate). Professor Konstantinos Matakos, King's College London, Fall 2017.
\item Teaching Assistant, \href{https://github.com/danilofreire/core-econ}{Principles of Economics I -- Microeconomics} (Undergraduate). Professor David Skarbek, King's College London, Winter 2017.
\end{itemize}

\section*{Skills}

\subsection*{Software}

\begin{itemize}
\item Python, R, Stata, SPSS, SQL, git, vimscript, Quarto, Markdown, HTML, \LaTeX{}.
\end{itemize}

\subsection*{Languages}

\begin{itemize}
\item Portuguese (native), English (fluent), Spanish (fluent), French (intermediate).
\end{itemize}

% \section*{Selected Additional Training}

% \begin{itemize}
% \item Transparent and Open Social Science Research, University of California, Berkeley, 2017. % https://www.futurelearn.com/certificates/al4bsct
% \item European Field Experiments Summer School, University of Palermo, 2017.
% \item Text Analysis Using R, London School of Economics, 2017.
% \item Data Science Specialisation, John Hopkins University on Coursera, 2015.
% \item Modern Regression Analysis, IPSA Summer School, 2012.
% \item Mixed Methods Design, IPSA Summer School, 2011.
% \item Policies for Growth, World Bank Institute, 2011.
% \end{itemize}

\section*{Service}

\begin{itemize}
    \item Referee: American Journal of Political Science, Civil Wars, Electoral Studies, Journal of Latin American Studies, Journal of Peace Research, Latin American Research Review, Leviathan, Political Behavior, Political Studies Review, Politikon, Princeton University Press, Revista Española de Ciencia Política, SAGE Open, The Social Science Journal, Swiss Political Science Review.
    \item Associate Editor: \href{https://onlinelibrary.wiley.com/journal/14682451}{International Social Science Journal}, 2024--present.
    \item Associate Editor: \href{https://www.nature.com/palcomms/}{Humanities \& Social Sciences Communications}, 2021--present.
    \item Co-editor: \href{https://www.revistas.usp.br/leviathan}{Leviathan}, University of São Paulo, 2012--2016.
\end{itemize}

\section*{Memberships}

\begin{itemize}
\item American Economic Association, American Political Science Association, Evidence in Governance and Politics, Global South Academic Network, Society for Policy Analytics, Society for Political Methodology
\end{itemize}

\section*{References}

\begin{itemize}

\item David Skarbek. Professor of Political Science and Political Economy, Department of Political Science and the Political Theory Project, Brown University. Email: \href{mailto:davidskarbek@gmail.com}{david\_skarbek@brown.edu}.
\item Fernando Limongi. Associate Professor, Department of Economics, Fundação Getulio Vargas. Email: \href{mailto:fernando.limongi@fgv.br}{fernando.limongi@fgv.br}.
\item Umberto Mignozzetti. Assistant Teaching Professor, Department of Political Science and the Computational Social Sciences Program, University of California, San Diego. Email: \href{mailto:umbertomig@ucsd.edu}{umbertomig@ucsd.edu}.
\item Gabriel Leon. Senior Lecturer, Department of Political Economy, King's College London. Email: \\ \href{mailto:gabriel.leon@kcl.ac.uk}{gabriel.leon@kcl.ac.uk}.
% \item Graham Denyer Willis. Senior Lecturer, Department of Politics and International Studies, University of Cambridge. Email: \href{mailto:gdw27@cam.ac.uk}{gdw27@cam.ac.uk}.
\end{itemize}

	\bigskip


\end{document}
